### 2014-03-17 src/analysis.Rnw
Update spellings, fix space etc.

\section{Analysis}
\label{sec:analysis}
For the purposes of comparing between the criteria, we computed the
linear correlation between sampled mutation score and full mutation score.
Since for the control sampling criteria, no mutants sampled implies none generated,
our model was
\[\mu_\{M_{all}|M_{reduced}\} = \beta_1 \times M_{reduced}\]
We reported the correlation for this linear regression. We also report the expected
multiplier factor $\beta_1$ for the sampled mutation score. This factor
determines the ease of detecting mutants in the sampling criteria. That is, if the
multiplier factor is small, then the sample mutation score was larger than
the full mutation score, and hence it was easier to detect mutants in the sample.

Next, for each criteria, we computed the reduction of mutants given by the
ratio between sampled mutants and total number of mutants.
We also compute standard deviation of the mutant reduction, which determines
the consistency of results. A large standard deviation suggests
that the mutant reduction ratio achieved is very much dependent on the
project. Therefore, as a heuristic, we suggest looking at only those methods which
have a mean reduction ratio at least twice the standard deviation.

>>>>

\section{Analysis}
\label{sec:analysis}
For the purposes of comparing between the criteria, we computed the
linear correlation between sampled mutation score and full mutation score.
Since for the baseline sampling criteria, no mutants sampled implies none generated,
our model was
\[\mu\{M_{all}|M_{reduced}\} = \beta_1 \times M_{reduced}\]
where $M_{all}$ is the mutation score of original mutation analysis and
$M_{reduced}$ is the mutation score of the sample.

We reported the correlation for this linear regression. We also report the expected
multiplier factor $\beta_1$ for the sampled mutation score. This factor
determines the ease of detecting mutants in the sampling criteria. That is, if the
multiplier factor is small, then the sample mutation score was larger than
the full mutation score, and hence it was easier to detect mutants in the sample.

Next, for each criterion, we computed the reduction of mutants given by the
ratio between sampled mutants and total number of mutants.
We also compute standard deviation of the mutant reduction, which determines
the consistency of results. A large standard deviation suggests
that the mutant reduction ratio achieved is very much dependent on the
project. Therefore, as a heuristic, we suggest looking at only those methods which
have a mean reduction ratio at least twice the standard deviation.

### 2014-03-17 src/methodology.Rnw
Update spellings, fix space etc.

\subsubsection{x\% selection}
The simplest sampling approach consisted of using x\% selection as suggested by
Budd~\cite{budd1980mutation}. In this criteria, we choose a specific
fraction of the complete set of mutants. This criteria also serves as a
control for verifying the effectiveness of other criteria.

@@

We used the formula by Zhang et al.~\cite{zhang2013ase},
\[sample(x) = floor (x + random(0..1))\]
to correctly sample decimal numbers.
Next, we modified this criteria slightly, and instead of
\textit{sample()} which uses probability to manage the decimal numbers,
we applied \textit{round()} to obtain the nearest whole number, which
was used as the number of samples to be chosen from the population.
Our aim was to \emph{remove} elements that were too simple. That
is, if the number of mutants dropped below a threshold determined by
the mutant reduction ratio, that program element did not contribute
any mutants to the final result.  Conceptually the idea is that mutants of more complex code have more discriminatory power (and may correspond better to real faults though we do not evaluate this concept).

@@

\subsubsection{Lines per element and variants}
Our previous research~\cite{gopinath2014code} found that statement coverage
was highly correlated with mutation score for a project. This immediately
suggests that perhaps choosing one mutant per line may be sufficient to achieve
a close approximation of the final mutation score. Further, statement deletion
has been researched previously~\cite{untch2009onreduced,deng2013empirical} and
has been found to reduce the number of mutants well, without an appreciable
decrease in effectiveness. This also provides a nice comparison with similar
numbers of mutants between operator selection and random sampling of mutants.

We next extended this approach to sample from each method instead, but
used the number of lines in the method as the number of mutants to be
sampled from it. This provided a test of the hypothesis of how
important a mutation sampling's relationship to simple code coverage
was. This was extended to class and project scope also.

@@

%{\bf ADG:  Could maybe make this clearer?}
% RG: Fixed with an example.

@@

For selective methods, we tried mutation operators suggested by Wong et al.~\cite{wong1995reducing}, Offutt et al.~\cite{offutt1996anexperimental,deng2013empirical}, % TODO Barbosa
 and, Namin et al.~\cite{siami2008sufficient}. Since Javalanche~\cite{javalanche} utilized operator selection mechanisms, we also compared the Javalanche operators for operator selection. Note that all of these techniques except
Javalanche have targeted C programs. Thus some of these operators
are sensible in C but not in Java programs. For example, deletion of return statement is tolerated in C, not in Java.
Moreover, there were a few operators that were not supported by the PIT, and could not be implemented easily.

\subsubsection{Criteria I}
For this criteria, we used the two operators \pitcb and \pitnc which are similar to those given by Wong. We did not have ABS operator available in PIT.
\subsubsection{Criteria II}
We used the operators given by Offutt et al. \Pitin, \Pitm, \Pitcb, \Pitnc. We did not have LCR available in PIT.
\subsubsection{Criteria III}
Those given by Javalanche \Pitnc, \Pitvmc, \Pitnvmc, \Pitm, \Pitic, \Pitemv. 
\subsubsection{Criteria IV}
Namin et al. used \Pitin, \Pitm, \Piti, \Pitnc. Many of these operators were not applicable in Java, and some not in PIT.
\subsubsection{Criteria V}
For this criteria, we utilized the approach suggested by
Offutt et al.~\cite{offutt1993experimental} where the most numerous operators
are discarded at each step.

>>>>

\subsubsection{x\% selection}
The simplest sampling approach consisted of using x\% selection as suggested by
Budd~\cite{budd1980mutation}. In this criteria, we choose a specific
fraction of the complete set of mutants. This criteria also serves as a
baseline for verifying the effectiveness of other criteria.

@@

We used the formula by Zhang et al.~\cite{zhang2013ase},
\[sample(x) = \lfloor x + random(0..1) \rfloor \]
to correctly sample decimal numbers.
Next, we slightly modified this criteria, and instead of
\textit{sample()} which uses probability to manage the decimal numbers,
we applied \textit{round()} to obtain the nearest whole number, which
was used as the number of samples to be chosen from the population.
The new strategy ignores program elements with small number of mutants.
This strategy can potentially guide mutation generation toward more
complex program elements.
That is, if the number of mutants dropped below a threshold determined by
the mutant reduction ratio, that program element would not contribute any
mutants to the final result.  Conceptually the idea is that mutants of more
complex code have more discriminatory power (and may correspond better to
real faults --- though we do not evaluate this concept).

@@

\subsubsection{Lines per element and variants}
Our previous research~\cite{gopinath2014code} found that statement coverage
was highly correlated with mutation score for a project. This immediately
suggests that perhaps choosing one mutant per line may be sufficient to achieve
a close approximation of the final mutation score. Further, statement deletion
has been researched previously~\cite{untch2009onreduced,deng2013empirical} and
has been found to reduce the number of mutants well, with negligible
decrease in effectiveness. This also provides a nice comparison with similar
numbers of mutants between operator selection and random sampling of mutants.

We extended sampling to levels coarser than methods, i.e. method, class, and
project. We sampled $n$ mutants from a method (class or project), where $n$
is the number of statements in the method (class or project).

This provided a test of the hypothesis of how important a mutation sampling's
relationship to simple code coverage is. This was extended to class and
project scope also.

@@

@@

For selective methods, we tried mutation operators
suggested by Wong et al.~\cite{wong1995reducing}, Offutt et
al.~\cite{offutt1996anexperimental,deng2013empirical}, and, Namin et
al.~\cite{siami2008sufficient}. Since Javalanche~\cite{javalanche} utilized
operator selection mechanisms, we also compared the Javalanche operators for
operator selection. Note that all of these techniques except Javalanche have
targeted C programs. Thus, some of these operators are sensible in C but not
in Java programs. For example, deletion of return statement is tolerated in C,
not in Java.  Moreover, there were a few operators that were not supported
by the PIT, and could not be implemented easily (as mentioned below).

\subsubsection{Criteria I} For this criteria, we used the two operators
\pitcb and \pitnc which are similar to those given by Wong. We did not have
ABS operator available in PIT.

\subsubsection{Criteria II} We used the operators given by Offutt et
al. \Pitin, \Pitm, \Pitcb, \Pitnc. We did not have LCR available in PIT.

\subsubsection{Criteria III} Those given by Javalanche : \Pitnc, \Pitvmc,
\Pitnvmc, \Pitm, \Pitic, \Pitemv.

\subsubsection{Criteria IV} Given by Namin et
al~\cite{siami2008sufficient}. Many of these operators were not applicable
in Java, and some not in PIT. The operators used by us were \Pitin, \Pitm,
\Piti, \Pitnc.

\subsubsection{Criteria V} In this criteria suggested by
Offutt et al.~\cite{offutt1993experimental} the most numerous operators are
discarded at each step. Our order was:
\Pitnvmc, \Pitnc, \Pitrc, \Pitdc, \Pitrv, \Pitic, \Pitcc, \Pitemv, \Pitvmc,
\Pitm, \Pitcb, \Piti, \Pitri, \Pitrs, \Pites, \Pitin.

### 2014-03-17 src/results.Rnw
move data to last
Update spellings, fix space etc.

Our results for random sampling over program elements using $sample(x)$
are given in Table~\ref{tbl:xselsample}. The result of the variation using
$round(x)$ is given in Table~\ref{tbl:xselround} and that using $ceil(x)$
is given in Table~\ref{tbl:xselceil}. The left tables show results from the
original set, while right tables show results from generated set.  The first
column in each table provides the scope of sampling: per project, per class,
per method, or per line. The second column ($\div$) provides the fraction
involved. The third column contains the $R^2$ value obtained between the
mutation score of the sampling criteria used and the full mutation score.
The fourth column ($\mu_{red}$) contains the mutant reduction factor.
This is the average of total mutants produced divided by the number of
mutants sampled by the criteria. The fifth column ($\sigma_{red}$) contains
the standard deviation of the same. A few of the projects did not return
any value for certain sampling criteria for particular mutation reduction
fractions. The sixth column contains the number of projects that actually
had valid values for the criteria being considered. The seventh column
($\beta_1$) is the average multiplier between the sampled mutation score
and the full mutation score.

@@

>>>>

Our results for random sampling over program elements using $sample(x)$
are given in Table~\ref{tbl:xselsample}. The result of the variation using
$round(x)$ is given in Table~\ref{tbl:xselround} and that using $ceil(x)$
is given in Table~\ref{tbl:xselceil}. The left tables show results from the
original set, while right tables show results from generated set.  The first
column in each table provides the scope of sampling: per project, per class,
per method, or per line. The second column ($\div$) provides the fraction
involved. The third column contains the $R^2$ value obtained between the
mutation score of the sampling criteria used and the full mutation score.
The fourth column ($\mu_{red}$) the mutant reduction factor,
which is the average of total mutants divided by the number of
mutants sampled. The fifth column ($\sigma_{red}$) is the standard deviation
of the same. As we explained in the analysis, the sixth column contains
the valid responses obtained.  The seventh column ($\beta_1$) is the
multiplier factor (coefficient reported by the regression.)

@@

Our data will be available for replication on publication~\cite{data}
%\footnote{Available on publication}.
